\plaintitle

### 2015-11-07 Paper/paper.tex
Removed \cleardoublepage command
Removed some parts of the RRL to shorten it a bit and be closer to specifications

The UPLB University Data Resource Network is another system used in UPLB. It was
created in 2003 and was also designed to be able to support modules. Gimotea (2003) was the
one who developed the Curricular, Degree Course, Class Schedules, and Room Assignment
Module which gave it functionalities similar to those that registration systems have like the
manipulation of schedules and rooms for classes and courses.
After a few years, Javier, et al. (2005) developed the first version of UPLB’s Online
Registration System called SystemOne. This system was also extensible through modularity. In
this version, SystemOne used the Java programming language for implementing the Enlistor and
Registrar module, PHP 5 for the Department module and MySQL as the Database Management
System (DBMS).

Because SystemOne was designed to be extensible through its support for modules, various
modules for it has been developed around the same time as the development of original
SystemOne. Curativo, et al. (2005) developed a web service module so that SystemOne can be
accessible using a web browser. Before that, users had to use the Java application for SystemOne
for them to be able to access it. Cardenas, et al. (2005) also developed another module called the
Data Manager Interface (DMI) which was responsible for allowing SystemOne to access a
Database Management System (DBMS) and converting data given by the Office of the
University Registrar through the REGIST system into a database that can be understood by
SystemOne. Both of these modules also used the Java programming language and supported the
MySQL DBMS.

In the year 2010, the development of the UPLB SystemOne V2 began. This version also
used the Java programming language and the MySQL DBMS and was also modular. However,
the difference of this new system from the previous system was that even the core functions were
divided into modules and was developed separately.

Payoyo (2010) developed the Announcement, Registrar and Observer Module for
SystemOne V2 which allowed support for announcement and gave representatives from the
registrar an interface to manage the courses to be offered among other things. Granada (2010)
developed the Subject Planner and Student’s Checklist which gave students the ability to view
their checklist and plan their schedule of subjects.

At the same time, Guevarra (2010) developed a Mobile Bluetooth Interface for Nokia 60
Series Smartphones using Symbian C++. This allowed users of the Nokia 60 Series Smartphones
to access SystemOne on their smartphones.

@@

Unfortunately, it is now a known fact that Java is rather slow compared to the alternatives.
Jelovic (n.d.) stated in one of his online articles that “anybody that has ever used a non-trivial
Java program or has programmed in Java knows that Java is slower than native programs written
in C++”. This is just one among the number of criticisms that Java receives when it comes to its
speed. Despite this, Java is known to be easy to use and was designed to be good for
network-based applications.

Another programming language used in the implementations of SystemOne is the PHP
programming language. This programming language is also known to be slow when it comes to
large-scale web applications. What more is that the flavor of PHP that was used in the third
version called Suhosin is known to be a bit slower than than the original PHP.

@@

The system will be designed to support HTTP Requests from specific domains
where the frontend code will be stored. This is to be able to outsource the load
added by frontend data being served as it will take a significant amount of
networking bandwidth to serve the images and scripts included. This will also
allow the frontend to have heavier images and scripts without affecting the 
performance of the main server.

@@

The frontend will be a static web application that fires REST requests to the
server. The Javascript Object Notation (JSON) will be used to specify parameters
for commands that require sending non-anonymous data while a normal GET request
can be used for reading data. The frontend will also have an enlistment queue
where the user can setup which subjects he/she would like to enlist and then
send them as a batch to the server. This would lessen the number of connections
that the server will receive lessening the number of threads running in the 
backend.

@@

\cleardoublepage

>>>>

After a few years, Javier, et al. (2005) developed the first version of UPLB’s Online
Registration System called SystemOne. This system was also extensible through modularity. In
this version, SystemOne used the Java programming language for implementing the Enlistor and
Registrar module, PHP 5 for the Department module and MySQL as the Database Management
System (DBMS).

In 2010, the development of the UPLB SystemOne V2 began. This version also
used the Java programming language and the MySQL DBMS and was also modular. However,
the difference of this new system from the previous system was that even the core functions were
divided into modules and was developed separately.

@@

@@

The system will be designed to support HTTP Requests from specific domains
where the frontend code will be stored through the Access-Control-Allow-Origin header. 
This is to be able to outsource the load added by frontend data being served as 
it will take a significant amount of networking bandwidth to serve the images and
scripts included. This will also allow the frontend to have heavier images and 
scripts without affecting the performance of the main server.

@@

The frontend will be a static web application that fires REST requests to the
backend server. The Javascript Object Notation (JSON) will be used to specify parameters
for commands that require sending non-anonymous data while a normal GET request
will be used for reading anonymous data. The frontend will also have an enlistment queue
where the user can setup which subjects he/she would like to enlist and then
send them as a batch to the server. This would lessen the number of connections
that the server will receive lessening the number of threads running in the 
backend.

The design for the frontend will try to follow Google's Material Design 
Specification although not strictly. Along with this, it shall support mobile
platforms by implementing Responsive Design.

@@

%\cleardoublepage
